---
title: "Upload a dataset"
#runtime: shiny_prerendered
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#library(shiny)
```

### Example
A dataset with two conditions and three replicates each would look like this:

```{r tmp, echo = F}
m <- matrix(rnorm(60, 200, 50), 6, 6)
rownames(m) <- paste0("Protein", LETTERS[1:6])
colnames(m) <- paste0(rep(LETTERS[1:2], each=3), "_", rep(1:3))
m
```


## Expected format

The first column in the data file should contain the *identifiers.* Currently, the following identifier types are accepted:

Identifier | Examples
------------- | ------------- 
UniProtKB | A1L4H1, A5A3E0, A6NMZ7, A8TX70, O00142
Entrez Gene ID  | 284297 728378 131873 256076 7084
Gene Symbol  | SSC5D  POTEF  COL6A6 COL6A5 TK2
Ensembl Gene ID  | ENSG00000179954 ENSG00000196604 ENSG00000206384 ENSG00000172752 ENSG00000166548
Ensembl Protein ID  | ENSP00000467252 ENSP00000386786 ENSP00000351310 ENSP00000309762 ENSP00000440898

A header row is expected, where each column corresponds to a sample name in the format *condition_replicate*.




